\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-29 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: minor cleanup
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64929 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@

\author{
Yann Chemin\inst{2},
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
Martin Landa\inst{4},
S\"{o}ren Gebbert\inst{5},
Pietro Zambelli\inst{3},
Markus Neteler\inst{6}, and
Peter L\"{o}we\inst{7}
Margherita Di Leo\inst{8}
}
\institute{
\instlist{1}NCSU, USA,
\instlist{2}IWMI, Sri Lanka,
\instlist{3}EURAC, Italy,
\instlist{4}FCE CTU in Prague, Czech Republic,
\instlist{5}TICSA, Germany,
\instlist{6}CRI, FEM, Italy,
\instlist{7}GNLST, Germany
\instlist{8}EC-JRC, Italy
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS as Temporal GIS}}{
The time dimension was introduced in GRASS GIS version 7 for raster, 3D raster and
vector map layers, transforming it into a full featured temporal GIS (Gebbert and Pebesma, 2014 \cite{Gebbert20141}).
Time series of map layers are managed in space time datasets, a new data type in GRASS GIS.
Based on the GRASS GIS Temporal Framework, more than 45 modules were implemented to manage, analyze, process
and visualize space time datasets. The temporal enabled GRASS GIS is able to efficiently
handle more than 100.000 map layers. It was used to analyze the
European Climate Assessment \& Dataset ECA\&D (Haylock et al. \cite{Haylock2008_climate_series})
for climate change indicators.

@@

\blocksectiontitle{Acknowledgements}
Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS}
% http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf

@@

GRASS GIS project is a Open Source Geospatial Foundation (OSGeo) project and is using OSGeo infrastructure for websites and repositories.

>>>>

% EGU: http://meetingorganizer.copernicus.org/EGU2015/posters/17174
%      http://meetingorganizer.copernicus.org/EGU2015/EGU2015-8314-7.pdf

@@

\author{
Yann Chemin\inst{2},
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
Martin Landa\inst{4},
S\"{o}ren Gebbert\inst{5},
Pietro Zambelli\inst{3},
Markus Neteler\inst{6},
Peter L\"{o}we\inst{7}, and
Margherita Di Leo\inst{8}
}
\institute{
\instlist{1}NCSU, USA;
\instlist{2}IWMI, Sri Lanka;
\instlist{3}EURAC, Italy;
\instlist{4}FCE CTU in Prague, Czech Republic;
\instlist{5}TICSA, Germany;
\instlist{6}CRI, FEM, Italy;
\instlist{7}GNLST, Germany;
\instlist{8}EC-JRC, Italy
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS as Temporal GIS}}{
The time dimension was introduced in GRASS GIS version 7 for raster, 3D raster and
vector map layers, transforming it into a full featured temporal GIS (Gebbert and Pebesma, 2014 \cite{Gebbert20141}).
Time series of map layers are managed in space time datasets, a new data type in GRASS GIS.
Based on the GRASS GIS Temporal Framework, more than 45 modules were implemented to manage, analyze, process
and visualize space time datasets. The temporal enabled GRASS GIS is able to efficiently
handle more than 100.000 map layers. It was used to analyze the
European Climate Assessment \& Dataset ECA\&D (Haylock et al. \cite{Haylock2008_climate_series})
for climate change indicators.

@@

\blocksectiontitle{Acknowledgements}
Matthew Horvath for \emph{Spill impacts from coal ash pond using GRASS GIS};
% http://www4.ncsu.edu/~jcfounta/Summer14Posters/horvath.pdf

@@

GRASS GIS project is a Open Source Geospatial Foundation (OSGeo) project and is using OSGeo infrastructure for Web site and code repository.
